---
title: "Homework 6"
author: Maya Bunyan
output: github_document
---

This my solution to Homework 6!

```{r setup, include=FALSE}
library(tidyverse)
library(modelr)
library(p8105.datasets)

knitr::opts_chunk$set(
  fig.width = 6,
  fig.asp = .6,
  out.width = "90%"
)

theme_set(theme_minimal() + theme(legend.position = "bottom"))

options(
  ggplot2.continuous.colour = "viridis",
  ggplot2.continuous.fill = "viridis"
)

scale_colour_discrete = scale_colour_viridis_d
scale_fill_discrete = scale_fill_viridis_d

set.seed(1)
```


# Problem 1


```{r}
homicide_df = 
  read_csv("data/homicide-data.csv", na = c("", "NA", "Unknown")) %>% 
  mutate(
    city_state = str_c(city, state, sep = ", "),
    victim_age = as.numeric(victim_age),
    resolution = case_when(
      disposition == "Closed without arrest" ~ 0,
      disposition == "Open/No arrest"        ~ 0,
      disposition == "Closed by arrest"      ~ 1)
  ) %>% 
  filter(
    victim_race %in% c("White", "Black"),
    city_state != "Tulsa, AL") %>% 
  select(city_state, resolution, victim_age, victim_race, victim_sex)
```

Start with one city.

```{r}
baltimore_df =
  homicide_df %>% 
  filter(city_state == "Baltimore, MD")
glm(resolution ~ victim_age + victim_race + victim_sex, 
    data = baltimore_df,
    family = binomial()) %>% 
  broom::tidy() %>% 
  mutate(
    OR = exp(estimate),
    CI_lower = exp(estimate - 1.96 * std.error),
    CI_upper = exp(estimate + 1.96 * std.error)
  ) %>% 
  select(term, OR, starts_with("CI")) %>% 
  knitr::kable(digits = 3)
```

Try across cities

```{r}
models_results_df = 
  homicide_df %>% 
  nest(data = -city_state) %>% 
  mutate(
    models = 
      map(.x = data, ~glm(resolution ~ victim_age + victim_race + victim_sex, data = .x, family = binomial())),
    results = map(models, broom::tidy)
  ) %>% 
  select(city_state, results) %>% 
  unnest(results) %>% 
  mutate(
    OR = exp(estimate),
    CI_lower = exp(estimate - 1.96 * std.error),
    CI_upper = exp(estimate + 1.96 * std.error)
  ) %>% 
  select(city_state, term, OR, starts_with("CI")) 
```


```{r}
models_results_df %>% 
  filter(term == "victim_sexMale") %>% 
  mutate(city_state = fct_reorder(city_state, OR)) %>% 
  ggplot(aes(x = city_state, y = OR)) + 
  geom_point() + 
  geom_errorbar(aes(ymin = CI_lower, ymax = CI_upper)) + 
  theme(axis.text.x = element_text(angle = 90, hjust = 1))
```


# Problem 2

Import and tidy the data

```{r}
baby_df = 
  read_csv("./data/birthweight.csv") %>%
  mutate(
    babysex = case_when(
      babysex == 1 ~ "Male",
      babysex == 2 ~ "Female"),
    mrace = case_when(
      mrace == 1 ~ "White",
      mrace == 2 ~ "Black",
      mrace == 3 ~ "Asian",
      mrace == 4 ~ "Puerto Rican",
      mrace == 8 ~ "Other",
      mrace == 9 ~ "Unknown"),
    frace = case_when(
      frace == 1 ~ "White",
      frace == 2 ~ "Black",
      frace == 3 ~ "Asian",
      frace == 4 ~ "Puerto Rican",
      frace == 8 ~ "Other",
      frace == 9 ~ "Unknown"),
    malform = case_when(
      malform == 0 ~ "Absent",
      babysex == 1 ~ "Present")
  ) %>%
  mutate(
    mrace = as.factor(mrace),
    frace = as.factor(frace),
    babysex = as.factor(babysex),
    malform = as.factor(malform)
  )
```


Based on the variables in the dataset, I think that a model for the baby's birth weight should have mother's age at delivery, number of live births prior to pregnancy, and average number of cigarettes smoked as predictors. I will start by creating my model:

```{r}
my_model = 
  lm(bwt ~ momage + parity + smoken, data = baby_df) 
my_model_results = 
  my_model %>%
  broom::tidy()
```

From the tidied output, I see that the p-value for the previous live births predictor is not significant. 


Plot of residuals again fitted values.

```{r}
baby_df %>% 
  modelr::add_residuals(my_model) %>% 
  modelr::add_predictions(my_model) %>%
  ggplot(aes(x = pred, y = resid)) + 
  geom_point()
```

Create two more models.
```{r}
main_effects_model = lm(bwt ~ blength + gaweeks, data = baby_df)
main_effects_model_results = main_effects_model %>% broom::tidy()

interaction_model = lm(bwt ~ bhead*blength*babysex, data = baby_df)
interaction_model_results = interaction_model %>% broom::tidy()
```

Comparison in terms of the cross-validated prediction error.
```{r}
baby_df_cross = 
  crossv_mc(baby_df, 100)

baby_df_cross = 
  baby_df_cross %>%
  mutate(
    my_model = map(train, ~lm(bwt ~ momage + parity + smoken, data = baby_df)),
    main_effects_model = map(train, ~lm(bwt ~ blength + gaweeks, data = baby_df)),
    interaction_model = map(train, ~lm(bwt ~ bhead*blength*babysex, data = baby_df))
  ) %>%
  mutate(
    rmse_my_model = map2_dbl(my_model, test, ~rmse(model = .x, data = .y)),
    rmse_main_effects = map2_dbl(main_effects_model, test, ~rmse(model = .x, data = .y)),
    rmse_interaction = map2_dbl(interaction_model, test, ~rmse(model = .x, data = .y)))

baby_df_cross %>% 
  select(starts_with("rmse")) %>% 
  pivot_longer(
    everything(),
    names_to = "model", 
    values_to = "rmse",
    names_prefix = "rmse_") %>% 
  mutate(model = fct_inorder(model)) %>% 
  ggplot(aes(x = model, y = rmse)) + geom_violin()

```

